Quantifying the global film festival circuit: networks, diversity and value creation

### 2023-02-08 cudan/paperplots.qmd
update

A listers are circles, B listers are crosses. 618 festivals, incl 132 series with 2+ events, 32700 unique films, 42365 festival-film pairs

@@

@@

25674 unique films, 572 unique fests, 34858 filmfest pairs, after final filter.

@@

24580 unique films, 543 unique fests, 42902 filmfest pairs, after final filter

@@

26906 unique films, 580 unique fests, 52811 filmfest pairs, after final filter

@@

    Deviance Residuals: 
        Min       1Q   Median       3Q      Max  
    -1.5794  -0.2952  -0.0879  -0.0144   5.6632

    Coefficients:
                  Estimate Std. Error  z value Pr(>|z|)    
    (Intercept)    1.03888    0.03848   26.995  < 2e-16 ***
    timedist      -1.63251    0.01564 -104.401  < 2e-16 ***
    class_bothAA   0.13604    0.03845    3.538 0.000403 ***
    class_bothBB  -0.15953    0.02515   -6.342 2.26e-10 ***
    genre         -5.90956    0.18649  -31.689  < 2e-16 ***
    lang          -4.94911    0.22468  -22.027  < 2e-16 ***
    geomean       -1.16421    0.23381   -4.979 6.38e-07 ***
    eventloc       1.17418    0.14601    8.042 8.84e-16 ***
    eventfilmdist -2.88983    0.30467   -9.485  < 2e-16 ***
    ---
    Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

    (Dispersion parameter for binomial family taken to be 1)

        Null deviance: 77718  on 146610  degrees of freedom
    Residual deviance: 48931  on 146602  degrees of freedom
    AIC: 48949

@@

    Coefficients:
                  Estimate Std. Error t value             Pr(>|t|)    
    (Intercept)    1.51365    0.02393  63.252 < 0.0000000000000002 ***
    timedist      -0.02539    0.01281  -1.983               0.0475 *  
    class_bothAA   0.16847    0.02430   6.933     0.00000000000466 ***
    class_bothBB  -0.08251    0.01741  -4.739     0.00000220276470 ***
    genre         -1.46203    0.14899  -9.813 < 0.0000000000000002 ***
    lang          -1.35904    0.16252  -8.362 < 0.0000000000000002 ***
    geomean       -0.17614    0.17612  -1.000               0.3173    
    eventloc      -0.18121    0.10436  -1.736               0.0825 .  
    eventfilmdist -0.52085    0.22052  -2.362               0.0182 *  
    ---
    Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

    Residual standard error: 0.5569 on 4944 degrees of freedom
    Multiple R-squared:  0.07302,   Adjusted R-squared:  0.07152 
    F-statistic: 48.68 on 8 and 4944 DF,  p-value: < 0.00000000000000022

>>>>

A listers are circles, B listers are crosses.

```{r}
attr(nodelist, "info") %>% cat
```

@@

Without any links, degree=0:
```{r}
nodelist %>% filter(degree==0)
```

@@

```{r}
cat(attr(festgenrevecs, "info"))
```

@@

```{r}
cat(attr(festlangvecs, "info"))
```

@@

```{r}
cat(attr(festcountryvecs, "info"))
```

@@

```{r}
glm(linked~timedist+class+genre+lang+geomean+eventloc+eventfilmdist,family = "binomial", 
        data=linkdat %>% select(-weight) %>% {.[complete.cases(.),]} ) %>% summary %>% print

@@

```{r}
lm(log(weight)~timedist+class+genre+lang+geomean+eventloc+eventfilmdist, 
        data=linkdat %>% filter(!is.na(weight), weight>1, weight<40) %>% {.[complete.cases(.),]} ) %>% summary %>% print
```
